\begin{acknowledgments}

The researchers gratefully acknowledge the support and guidance of all individuals who contributed to the completion of this study. We sincerely thank \textbf{Ms. Rosel Onesa}, OIC Dean, College of Computer Studies, for her encouragement and administrative support; \textbf{Ma'am Kaela Marie Fortuno}, our thesis adviser, for her guidance and valuable insights; \textbf{Mr. Juan Rodrigo Badiola}, our consultant, for his expert advice; and \textbf{Ms. Jayvie Margate}, our grammarian, for her careful review and assistance in improving the quality of this manuscript.

We also extend our gratitude to the honorable panelists, \textbf{Ma'am Tiffany Lyn O. Pandes}, \textbf{Sir Freddie B. Prianes}, and \textbf{Sir Joseph Jessie S. Onate}, for their constructive comments and helpful suggestions during the defense. We likewise thank \textbf{Ms. Marri Grace Morata}, the Secretary, for her assistance and encouragement, and the Registrar’s Office for their prompt support in providing the necessary documents for this study. Their cooperation and professionalism greatly contributed to the smooth completion of our academic requirements. The insights and logistical assistance they provided strengthened the overall quality and credibility of this research.

Above all, we thank the researchers’ loving parents for their unwavering love, support, and sacrifices throughout this journey. Their constant encouragement, guidance, and motivation inspired us to persevere through challenges and remain focused on our goals. Most importantly, we offer our sincerest gratitude to Almighty God for the wisdom, strength, and guidance that made this study possible. His blessings sustained us throughout the entire research process.


\end{acknowledgments}